Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2014-10-09 misc/SI_thesis.tex
supporting info reading

\section{A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST A LONG SECTION TITLE FOR TOC CONTENT LINE WRAPPING TEST TEST TEST}

@@

The average distance between dopant atoms is cubed root of concentration, $d = (10^{18} cm^{-3})^{-1/3} = 10nm$.

@@

for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450) = 1.4E16 cm^{-3}$.

@@

Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows. Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model. d electrons show intermediate character.

@@

@@

Raman assignment of \ce{WO3}

XRD assignment of \ce{WO3}

@@

\ce{Na2W2O7} Raman. \cite{Knee1979}

\ce{WO3}, \ce{WP3.H2O}\cite{Daniel1987}

@@

@@

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$, in units of \si{\cm^2\per\coulomb}) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
\begin{equation}
x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
\end{equation}
where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant.
The color center density, $c$, is then obtained using formula
\begin{equation}
c= \frac{x M_\ce{WO3}N_A}{\rho}
\end{equation}
where $N_A$ is Avogadro number, $\rho$ is density of film.

battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
cathodic coloration:
anodic coloration:
The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channelling.
ref54,60,65,66,200,209,

@@

first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
the importance of contact, and avoiding moisture.

The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibibly arising from sulfur vacancy.

@@

The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
thionine peaks at 600nm.
MB forms dimers in aqueous solution,
\ce{
2MB <=>[K_D] (MB)_2
}
A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration:
\[
2K_D [MB]^2 + [MB] - [MB]_{total} = 0
\]
MB adsorption on metal oxides. Monomer size is less than 1.5nm.
Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23V and 0.817V versus NHE at pH 0 and pH 7, respectively.

@@

Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.

@@

\ce{WO3} high temperature phase. \cite{Vogt1999}
tungsten bronzes \cite{Wiseman1976}

Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}

\ce{WO2} NWs synthesis and raman \cite{Ma2005}.

@@

sodium tungstates raman \cite{Redkin2010}

@@

\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
broad peak between 750-780 cm-1.

@@

optical characterization of WOx film.\cite{Valyukh2010a}

E-beam penetration \cite{Kanaya2002}

@@

>>>>

\section{KK, optics modeling, doping}

@@

The average distance between dopant atoms is cubed root of concentration, $d = (10^{18})^{-1/3}$ \si{cm^{-3}}$^{-1/3}$ = 10 nm.

@@

for p-type silicon, when the conductivity $\sigma = 1 (ohm cm )^{-1}$, the doping level is
$N_A = \frac{\sigma}{q \mu_p}= 1 / (1.6E-19 \times 450)$ = 1.4E16 \si{cm^{-3}}.

@@

Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows. Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker. For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model. d electrons show intermediate character.

@@

sodium tungsten bronzes, DRS from 335 nm to 1250 nm show \ce{Na_{0.3}WO3} exhibits absorption peak at about 650 nm.\cite{Brown1954}

oxygen deficiency, electron carrier con about $5\times10^{18}$ \si{cm^3}, absorption edge at 2.7 eV attributed allowed transition. absorption in infrared region observed but not rigorously resolved: donor level in the forbidden gap near VB, or thermally excited electrons in CB. Absorption increase when oxygen vacancy is created. Resistivity increase as heated up. \cite{Berak1970}

A systematic study of optical and electrical properties of \ce{WO3} thin film.\cite{Deb1973} Film density 6.5 \si{g\per cm^3}, substantial porosity. \ce{WO3} become substoichiometric at 1300-1500 K, and evaporate at a composition near \ce{WO_{2.96}}. $K \propor (h\nu - E_g)^2/h\nu$, indicating an allowed band to band transition, and 3.25 eV energy gap determined thereby. Refractive index $\epsilon_{st}$ of thin film \ce{WO3} found at 2.2, lower than that of single crystal value of 2.5; $n$ increases to 4.0 at absorption edge region, with $\alpha$ as high as $10^5$ \si{cm^{-1}}. So the color center can form in a thin layer of 100 nm; its density estimated by the Smakula's Equation:
\[
Nf = 0.89\times10^17\frac{n}{(n^2+2)^2} \alpha d
\]
where $f$ osc strength, n ref index, $\alpha$ in \si{cm^{-1}}, and d is the half width of absorption band. Assuming $f$ = 1, N to be $5\times10^{19}$ \si{cm^3}. 
Narrow conduction band proposed to explain the high energy peak at 4.39 eV and 5.25 eV. Impurity band when the ele wavefuntion overlap, the color center spacing comparable to lattice constant.

@@

Raman assignment of \ce{WO3}
XRD assignment of \ce{WO3}

@@

\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na4W4O13} & &\\
\ce{Na5W14O44} & & this work
\bottomrule
\end{tabular}
Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

Nanoscale \ce{WO3} Raman.\cite{Boulova2002}

\ce{WO3} and sub-wo3 conductivity vs temp. \cite{Sahle1983}

Delichere1988coloured states

\ce{W18O49} reflectivity, carrier density $1.87\times10^{22}$ \si{cm^{-3}}, quasi-free carrier reflection of Drude type, \cite{Brandt1981}

@@

carrier density estimation, the stoichiometry of tungsten bronze was calculation from the inserted charge by Faraday's Law. Na diffuses slower than H+, accumulating at the surface of wo3 film and preventing further intercalation.\cite{Dini1996}

\[
m = \frac{Q}{F} \frac{M}{z},
\]
where $m$ is the mass of substance at an electrode in gram, $Q$ is the total charge transferred; F is Faraday constant; $M$ is molar mass; $z$ is the valency number of ions.

The degree of \ce{H^+} intercalation, $x$, is determined by integrating cathodic current, and given by
\begin{equation}
x = \frac{Q}{F}\frac{M_\ce{WO3}}{m_f}
\end{equation}
where $m_f$ is the mass of film, $M_\ce{WO3}$ is the molar mass of \ce{WO3*1/3H2O}, and F is Faraday's constant. 
The color center density, $c$, is then obtained using formula
\begin{equation}
c= \frac{x \rho N_A}{M_\ce{WO3}}
\end{equation}
where $N_A$ is Avogadro number, $\rho$ is density of film.

During the test of ECD, constant current source is often used. The total charge $Q$ is then $It$. Charge density, the diffusion of \ce{Na+},

@@

The coloration efficiency (CE) represents the change in the optical density (OD) per unit charge density ($Q/A$ in unit of \si{\coulomb}\per\cm^2) during switching and can be calculated according to the formula:
\begin{equation}
CE = \frac{\Delta~OD}{(Q/A)} [cm^2/C],
\end{equation}
where OD = $log(T_{bleach}/T_{color})$. The EC and optical density depend on the wavelength and are usually higher in the near IR than in the visible region.
Using Ohm's law($U_s = IR = RQ/t_s$) with switch voltage $U_s$, resistance R and surface area A, switching time $t_s$ could be estimated as
\begin{equation}
t_s = \Delta~OD\cdot A \cdot R /(CE\cdot U_s).
\end{equation}

battery and ECD.\cite{Granqvist2012} electrolyte: PVB (poly vinyl buteral).
alternative materials and design: organic, Prussian Blue as EC materials, metal hydrides, suspended particle device, liquid crystal, electroplating,
challenges: large area nanoporosity, transparent conducting contact, electrolyte with good ionic conductivity and poor electronic conductivity, stable under UV; assembly and large scale manufacturing;
cathodic coloration:
anodic coloration:
The coloration mechanism: \ce{MO6} octahedrons lead to $e_g$ and $t_{2g}$ level and ion channeling.
ref54,60,65,66,200,209,

@@

first demonstration of \ce{WS2} NT n-type FET. \cite{Levi2013}
the importance of contact, and avoiding moisture. The calculated carrier concentration is about $10^{19}cm^{-3}$, a highly doped semiconductor, possibly arising from sulfur vacancy.

@@

The oxidized form of MB, \ce{MB.^+} has peak at 520nm, which is stable in acidic solution, but decomposes irreversibly in slight alkaline solution(pH = 9).
thionine peaks at 600nm.
MB forms dimers in aqueous solution,
\ce{
2MB <=>[K_D] (MB)_2
}
A typical value of $K_D$ is 3970 1/M. A quadratic equation can be solved to obtain the monomer concentration:
\[
2K_D [MB]^2 + [MB] - [MB]_{total} = 0
\]
MB adsorption on metal oxides. Monomer size is less than 1.5nm.
Logarithmic acid dissociation constant $pK_a= -\log_10 \frac{[A^-][H^+]}{[HA]}$. The oxidation potential for \ce{H2O}-\ce{O2} couple is 1.23 V and 0.817 V versus NHE at pH 0 and pH 7, respectively.

@@

@@

\ce{WO3} high temperature phase. \cite{Vogt1999}

@@

@@

@@

optical characterization of WOx film.\cite{Valyukh2010a}
homogeneous optical properties of \ce{WO3} film,\cite{Valyukh2010a}

Tungsten bronze: \ce{AxWO3}, or \ce{AxW_{1-x}^{6+}W_x^{5+}O3}, 
Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR.

============================
E-beam penetration \cite{Kanaya2002}

@@

\ce{W_{18}O_{49}} Raman, IR shielding.\cite{Guo2012} \cite{Guo2011}
broad peak between 750-780 cm-1.
\ce{Na2W2O7} Raman. \cite{Knee1979}
Raman fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3.nH2O} were summarized in ref\cite{Daniel1987}.
Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}
sodium tungstates solution compounds Raman \cite{Redkin2010}
\ce{WO2} NWs synthesis and raman \cite{Ma2005}
tungsten bronzes \cite{Wiseman1976}
